---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# cebrapdata

<!-- badges: start -->
<!-- badges: end -->

`cebrapdata` is a simple R client for the [Cebrap](https://cebrap.org.br/)'s Brazilian Legislative Database, the main and oldest specialized source of legislative data in Brazil. With the package, querying, fetching, and storing data locally could be done fast with a few lines of code from R.


## Installation

For the time being, `cebrapdata` dev version can be installed from [GitHub](https://github.com/) using the [remotes](https://cran.r-project.org/web/packages/remotes/index.html) package:

```{r, eval = FALSE}
if(!require(remotes)) install.packages("remotes")
remotes::install_github("nipe-cebrap/cebrapdata")
```


## How does it work?

Under the hood, `cebrapdata` uses [RJDBC](https://cran.r-project.org/web/packages/RJDBC/index.html) to manage connections, abstract queries and fetch data from Cebrap's Database, making it easy to ingest Brazilian legislative data from R.


```{r, eval=FALSE}
library(cebrapdata)
```


## Requirements

To use the package, users need to select the appropriate MS-SQL Server JBDC driver from [Microsoft](https://docs.microsoft.com/pt-br/sql/connect/jdbc/download-microsoft-jdbc-driver-for-sql-server?view=sql-server-ver15). To speed up this proccess, `cebrapdata` already provides three different driver option: 

- `mssql-jdbc-9.2.1.jre8.jar`;
- `mssql-jdbc-9.2.1.jre11.jar`; and
- `mssql-jdbc-9.2.1.jre15.jar`

By default, `get_cebrap_table` and similar functions use `jre15` version to manage the connection to Cebrap's database, but this can be changed with the `driver` argument:

```{r, eval=FALSE}
# exemplae
```



...

# Credits

[NIPE-Cebrap](https://cebrap.org.br/nucleos/nucleo-instituicoes-politicas-e-eleicoes/) and [Fapesp](https://fapesp.br/) (proccess number #).

