---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# cebrapdata

<!-- badges: start -->
[![R-CMD-check](https://github.com/nipe-cebrap/cebrapdata/workflows/R-CMD-check/badge.svg)](https://github.com/nipe-cebrap/cebrapdata/actions)
<!-- badges: end -->

`cebrapdata` is a simple R client for the [Cebrap](https://cebrap.org.br/)'s Brazilian Legislative Database, the main and oldest specialized source of legislative data in Brazil. With the package, querying, fetching, and storing data locally could be done fast with a few lines of code from R.


## Installation

For the time being, `cebrapdata` dev version can be installed from [GitHub](https://github.com/) using the [remotes](https://cran.r-project.org/web/packages/remotes/index.html) package:

```{r, eval = FALSE}
if(!require(remotes)) install.packages("remotes")
remotes::install_github("nipe-cebrap/cebrapdata")
```


## How does it work?

Under the hood, `cebrapdata` manages connections, abstracts queries and fetches data from Cebrap's Database, making it easy to ingest Brazilian legislative data from R.

To start using the package, it is recommended that users create and store their credentials using the `store_credentials()` function:


```{r, eval=FALSE}
# Load the package
library(cebrapdata)

# Set credentials
store_credentials(login = "meulogin", password = "minhasenha")
```

R will store your credentials as environment variables so there will be no need to re-enter these information again in the future (besides, this is a safer way to store credentials). After that, make a connection to Cebrap's Database with `set_connection()` and start fetching data with `get_cebrap_table()`:

```{r, eval=FALSE}
# Set connection
conn <- set_connection()

# Request a table
senadores <- get_cebrap_table(conn, "tbl_Sen")
```



## Requirements

To install and use `cebrapdata`, [Java Runtime Environment (JRE)](https://www.java.com/pt-BR/download/manual.jsp) and [Java JDK](https://www.oracle.com/br/java/technologies/javase/javase-jdk8-downloads.html) must be previously installed on your computer or server (click on these links to install the apropriate version to your system).

In case you face a problem installing these dependencies or the `cebrapdata`, submit an issue with more details.

### Other R packages

To work, `cebrapdata` depends on [rJava](https://cran.r-project.org/web/packages/rJava/index.html) and RJDBC, which should be installed automacally when installing `cebrapdata` from R.

To use the package, users need to select the appropriate MS-SQL Server JBDC driver from [Microsoft](https://docs.microsoft.com/pt-br/sql/connect/jdbc/download-microsoft-jdbc-driver-for-sql-server?view=sql-server-ver15). `cebrapdata` already provides three different driver option: 

- `mssql-jdbc-9.2.1.jre8.jar`;
- `mssql-jdbc-9.2.1.jre11.jar`; and
- `mssql-jdbc-9.2.1.jre15.jar`

By default, `get_cebrap_table` and similar functions use `jre15` version to manage the connection to Cebrap's database, but this can be changed with the `driver` argument:

```{r, eval=FALSE}
# Change driver
conn <- set_connection(driver = "jre15")
```

If none of these default drivers work for you, there is the option to download a different one and use its filepath instead:

```{r, eval=FALSE}
# Change driver
conn <- set_connection(driver = "another-jdbc-driver.jar")
```


# Credits

[NIPE-Cebrap](https://cebrap.org.br/nucleos/nucleo-instituicoes-politicas-e-eleicoes/) and [Fapesp](https://fapesp.br/) (proccess number #).

